A Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}

### 2019-05-21 main.tex
Wrote outline.

% 通常のルール
The rules \TVar , \TAbs, and \TApp\ are almost same as those in simply typed lambda calculus 
if you ignore stage annotations and kind checking.
The rule \TVar\ means that a variable can appear only at the stage in which it is declared.
It checks the type of variable $x$, $\tau$, has the proper kind for terms, $*$.
\TAbs\ also checks the kind of the type.

@@

% \TConv
The main technical point of this paper is \TConv and type equivalence rules needed in \TConv.
This rule allows ut to replace a type with another type that is equivalent.
In a type system which includes dependent types, this kind of rule is essential
because two types which have different shapes may be equivalent.
For example, when we use a matrix type which have their sizes ($\textrm{Mat}\ n\ m$),
$\textrm{Mat}\ 5\ 3$ is equivalent to $\textrm{Mat}\ (4+1)\ (1+2)$ obviously.

@@

\subsubsection{Type Equivalence Rules}

>>>>

% 通常のルール
We show typing rules of \LMD in Figure \ref{fig:typing-rules}.
The rules \TVar , \TAbs, and \TApp\ are almost same as those in simply typed lambda calculus 
if you ignore stage annotations and kind checking.
The rule \TVar\ means that a variable can appear only at the stage in which it is declared.
It checks the type of variable $x$, $\tau$, has the proper kind for terms, $*$.
\TAbs\ also checks the kind of the type.

@@

% \TConv
The main technical point of this paper is \TConv\ and type equivalence rules needed in \TConv.
This rule allows ut to replace a type with another type that is equivalent.
In a type system which includes dependent types, this kind of rule is essential
because two types which have different shapes may be equivalent.
For example, when we use a matrix type which have their sizes ($\textrm{Mat}\ n\ m$),
$\textrm{Mat}\ 5\ 3$ is equivalent to $\textrm{Mat}\ (4+1)\ (1+2)$ obviously.

@@

\subsubsection{Type Equivalence Rules\\}

As mentioned above, type equivalence rules are needed in \LMD.
We show the rules in Figure \ref{fig:type-equivalence-rules}.

% 2つの設計手法と今回採用した理由

% \QCsp以外の説明

% \QCspの説明

 % mulmatの例
